Hierarchical Time Series Forecasting in Emergency Medical Services

### 2023-07-18 journal_correspondence/response_letter/response_letter_JSR.qmd

\textcolor{teal}{We have chosen the naive method as a benchmark due to its widespread usage and simplicity, making it easily understandable for users. Forecasts serve as inputs for various decision-making systems that frequently employ simulations, wherein it is common to utilize the empirical distribution of demand as a forecast. Additionally, the naive method has shown surprisingly high accuracy. Hence, any forecasting approach that can offer superior results compared to the naive method would validate its practical use, otherwise there is no necessity for employing more complex methods.}

@@

_Comment 4.2: In your discussion of ETS, you mention that the trend, seasonality, and error terms can take various forms, such as additive, multiplicative, or mixed. Can you specify which form you used for each of these components in your research and explain the reasoning behind your choice?_

**Response:** In response to your comment, we have included the following text in the revised version of the manuscript:

\textcolor{teal}{In our study, we use an automated algorithm to determine the suitable form for the trend, seasonality, and error terms in each time series. Specifically, we utilize the `ETS()` function in the fable package of R, which employs statistical criteria like Akaike's Information Criterion (AIC) to identify the optimal model for each time series. Given the large number of time series we work with (1530), it is impractical to manually select the appropriate form for each component in every time series. Consequently, the automated algorithm selects the most fitting components based on the unique characteristics of each individual time series. As a result, a combination of additive or multiplicative forms for the components are employed, depending on the specific attributes of each time series.}

@@

_Comment 4.3: In your research, the Generalized Linear Model (GLM) approach is used for forecasting. Can you provide the equation used for this approach in a concise form? Additionally, in your description of the Fourier terms, it is mentioned that they are used to capture yearly seasonality. Does your research also take into account monthly seasonality and if so, how is it captured? Furthermore, for yearly seasonality, what is the specific form of the Fourier term used?_

**Response:** Thank you for your comment. We have included the following text in revised manuscript to address your comment:

\textcolor{teal}{Suppose the time series is denoted by $y_1,\dots,y_T$, then the Poisson GLM can be written as}

\begin{align*}
  y_t &\sim \text{Poisson}(\lambda_t) \\
  \text{where}\qquad
  \log(\lambda_t) &= \bm{x}_t'\bm{\beta},
\end{align*}

\textcolor{teal}{and $\bm{x}_t$ is a vector of covariates, $\beta$ is a vector of coefficients, and $\lambda_t$ is the parameter of Poisson distribution. In our model, these include cubic splines for the time trend, day-of-week dummy variables (from Monday to Sunday), Fourier terms to capture the yearly seasonality, dummy variables indicating public holidays (1 when is public holiday, 0 otherwise), school holidays (1 when is school holiday, 0 otherwise) and Christmas Day (1 when is Christmas Day, 0 otherwise) and New Year's Day (1 when is New Year's Day, 0 otherwise). The Fourier terms are as defined in} @hyndman2021forecasting \textcolor{teal}{(Section 7.4). This model takes account of weekly seasonality and annual seasonality. Monthly seasonality is exceedingly rare in time series data, and does not occur in ambulance demand. There is no reason, for example, for incidents to occur more at some times of the month than others.}

@@

_Comment 4.4: Can you explain what “serial dependence” means in the TSGLM model in the context of EMS forecasting?_

**Response:** In the context of EMS forecasting, serial dependence refers to the situations where ambulance demand at one point in time are correlated with the demand at previous points in time. In other words, the past values of the time series influence the current values, and this influence can be modeled using a variety of techniques. The TSGLM model, for example, explicitly accounts for serial dependence by including lagged values of the ambulance demand in the model. This is important in EMS forecasting because it allows the model to capture patterns and trends in the data that are dependent on the history of the time series, and which are not captured via the predictor variables.

We have now included the following text in revised manuscript:

\textcolor{teal}{The Poisson TSGLM is similar to GLM with an aditional component accounting for serial dependence (i.e. autoregressive terms). The term serial dependence refers to situations where the ambulance demand at a given time exhibits correlation with the demand at previous time intervals. Put simply, past values of the time series influence the current values. TSGLM can be written as}

\begin{align*}
  y_t &\sim \text{Poisson}(\lambda_t) \\
  \text{where}\qquad
  \log(\lambda_t) &= (\bm{y}_{t-k}'+\bm{x}_t')\bm{\beta},
\end{align*}

\textcolor{teal}{${y}_{t-k}$ is a vector of k lagged values. The TSGLM model explicitly accounts for serial dependence by including lagged values (i.e. past values) of the ambulance demand in the model. This is important in EMS forecasting because it allows the model to capture patterns in the data that are dependent on the past values of the time series, which might not be captured via the predictor variables.}

\textcolor{teal}{We use the `tsglm()` function in the tscount package in R} [@JSSv082i05] \textcolor{teal}{to model the attended incidents. Again, the logarithmic link function is used to ensure that the parameter of Poisson distribution is always positive.}

@@

_Comment 4.5: It is clear that the naive method performed poorly in the results. Can you explain the reasoning behind its inclusion in the ensemble method? Have you also evaluated the performance of an ensemble method that combines forecasts from only ETS, GLM and TSGLM, without the naive method? I would be interested in seeing the results from this alternative ensemble method._

**Response:** We re-ran the results of our experiment with the naive method excluded and name it "Ensemble 2". We illustrated the results in the following plot. As the plot shows, excluding the naive from the ensemble deteriorates the performance overall, so we keep it in the ensemble and show the original plot in the revised manuscript.

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-accuracy
#| fig-width: 8
#| fig-height: 5
#| out.width: "100%"
library(knitr)
library(kableExtra)
library(ggthemes)
library(patchwork)
library(tidyverse)
rmsse <- readr::read_rds(here::here("results/rmsse.rds")) |> 
  mutate(msse = rmsse^2)
mase <- readr::read_rds(here::here("results/mase.rds"))
crps <- readr::read_rds(here::here("results/crps.rds")) |>
  pivot_wider(names_from = model, values_from = crps) |>
  group_by(method, h, series) |>
  mutate(across(where(is.numeric), ~ .x / naiveecdf)) |>
  ungroup()
crps <- crps |>
  pivot_longer(ensemble:tscount, names_to = "model", values_to = "crps")

accuracy <- bind_rows(
  rmsse |> mutate(measure = "msse", accuracy = rmsse^2),
  mase |> mutate(measure = "mase", accuracy = mase),
  crps |> mutate(measure = "crps", accuracy = crps),
) |>
  select(-rmsse, -mase, -crps)

# Plot of average accuracy vs week for each method for Total
acc_summary <- accuracy |>
  filter(
    series %in% c("Total", "Control areas", "Health boards"),
    method == "mint", model != "qcomb"
  ) |>
  mutate(model = case_when(
    model == "naiveecdf" ~ "Naive",
    model == "ets" ~  "ETS",
    model == "tscount" ~ "TSGLM",
    model == "iglm" ~ "GLM",
    model == "ensemble" ~ "Ensemble",
    model == "ensemble2" ~ "Ensemble2"
  )) |> 
  mutate(
    measure = factor(measure, levels = c("mase","msse","crps"), labels = c("MASE","MSSE","CRPS")),
    series = factor(series, levels = c("Total", "Control areas", "Health boards")),
    model = factor(model, levels = c("Naive", "ETS", "TSGLM", "GLM", "Ensemble", "Ensemble2")),
    week = factor(trunc((h - 1) / 7) + 1)
  ) |>
  group_by(week, model, measure, series) |>
  summarise(accuracy = mean(accuracy), .groups = "drop")

acc_summary |>
  ggplot(aes(x = week, y = accuracy, group = model, col = model)) +
  geom_line() +
  geom_point(size = .5) +
  facet_grid(measure ~ series, scales = "free_y") +
  labs(y = "Average accuracy", x = "Week ahead") +
  ggthemes::scale_color_colorblind() +
  ggthemes::theme_few()
```

@@

_Comment 5: In the first paragraph of section 3.3, you stated that the model development and hyper-parameter tuning process is conducted using the training data alone. Is this a commonly employed approach within the literature? From my understanding, when hyper-parameter tuning is involved, a dataset is typically divided into three sets: training, validation, and test sets. The training set is used to develop the model, the validation set is employed for tuning the parameters, and the test set is utilized to report the error measurement metric. Can you provide further clarification on this methodology and how it compares to the standard approach in the literature?_

**Response:** In machine learning applications, datasets might be divided into three sets: training, validation, and test sets, and the validation set is used to tune the hyperparameters of the model. But we use a more efficient approach than this, whereby we employ time series cross-validation [@hyndman2021forecasting,Section 5.10] to assess the forecast accuracy, and thus the use of a separate "validation dataset" becomes unnecessary. Time series cross-validation involves dividing the data into multiple training and testing sets based on the time series structure. Each testing set consists of a number of observations equal to the forecast horizon, and the corresponding training set only includes observations that occurred before the test set. This ensures that future observations are not used in constructing the forecast, making it more robust to evaluate forecast accuracy on new data. Therefore, we believe that our methodology is appropriate for time series forecasting and provides a more robust approach for evaluating forecast accuracy on new data.

@@

**Response:** To clarify, the forecasting horizon j represents the number of time periods ahead that we are forecasting, which is $j= 1,2,\dots, 84$ days in our study. We will make sure to include this information in the revised version of the paper.

In terms of the choice of accuracy measures, we chose MASE and MSSE because they are scale-independent. Using scale-independent measures like MASE and MSSE allows for more meaningful comparisons between time series at different levels and scales, as they are not affected by the magnitude of the data. This is particularly important in our study, as we have time series at various levels of the EMS hierarchy, which may have different scales and therefore different magnitudes of error. By using scale-independent measures, we can compare the accuracy of forecasts across the entire hierarchy in a more meaningful way.

MASE stands for Mean Absolute Scaled Error, and is a normalized measure of the mean absolute error (MAE) of the forecast relative to the naïve forecast, which is a simple forecasting method that uses the last observed value as the forecast for the next time period. Similarly, MSSE stands for Mean Squared Scaled Error and is a normalized measure of the mean squared error (MSE) of the forecast relative to the MSE of the naïve forecast.

\textcolor{teal}{The error metrics provided below consider a forecasting horizon denoted by j, representing the number of time periods ahead we are predicting. In our study, this forecasting horizon ranges from 1 to 84 days, $j= 1,2,\dots, 84$.}

\textcolor{teal}{Using of scale-independent measures, such as MASE and MSSE, enables more significant comparisons between time series at different levels and scales, as these measures are not influenced by the data's magnitude. This aspect holds particular importance in our study, as we work with time series at various levels of hierarchy. These time series show varying scales, resulting in different magnitudes of error. By employing scale-independent measures, we can meaningfully assess the forecast accuracy across the entire hierarchy, ensuring a more robust comparison.}

@@

_Comment 7: In the last paragraph of page 13, the Continuous Ranked Probability Score (CRPS) is mentioned as a metric that rewards sharpness and penalizes miscalibration. Can you provide an explanation of what these terms mean in the context of your problem or dataset? Additionally, in the definition of p_j, the forecasted probability distribution and true probability distribution are referenced. Can you explain how these are derived from the dataset? If a specific distribution is assumed, it would be helpful to be specific about it._

**Response:**  We have provided responses to each of the two separate questions below:

Calibration refers to the statistical consistency between the distributional forecasts and the observations. It measures how well the predicted probabilities match the actual probabilities. On the other hand, sharpness refers to the concentration of the forecast distributions --- a sharp forecast distribution results in narrow prediction intervals, indicating high confidence in the forecast. A model is well-calibrated if the predicted probabilities match the actual probabilities, and it is sharp if it is confident in its predictions. The CRPS rewards sharpness and calibration by assigning lower scores to forecasts with sharper distributions, and to forecasts that are well-calibrated. Thus, it is a metric that combines both sharpness and miscalibration into a single score, making it a useful tool for evaluating the performance of probabilistic forecasts. We chose the CRPS as one of our evaluation metrics because it provides a comprehensive assessment of the forecast quality and allows us to compare the performance of different models.

To generate forecast probability distributions, we did not assume a specific distribution; instead we used a form of bootstrapping, described in @panagiotelis2023probabilistic. This involves simulating 1000 future sample paths from each of the model, by bootstrapping the model residuals, taking into account the cross-sectional correlations between the different aggregated and disaggregated series. In this way, we can generate an empirical distribution of forecasts for each model. The ensemble forecast distribution is a simple mixture of these empirical distributions.

@@

The comparison between the forecast distribution and the observations is then used to calculate the CRPS. In this context, the "true probability distribution" has all its weight on the observed value, and zero elsewhere.

We have now updated the explanation of CRPS along the lines described above.

We have added the following text to section 3.2 in the revised version of the paper:

\textcolor{teal}{To generate forecast probability distributions using above methods, we use a form of bootstrapping, described in} @panagiotelis2023probabilistic. \textcolor{teal}{This involves simulating 1000 future sample paths from each of the model, by bootstrapping the model residuals, taking into account the cross-sectional correlations between the different aggregated and disaggregated series. In this way, we can generate an empirical distribution of forecasts for each model. The ensemble forecast distribution is a simple mixture of these empirical distributions.}

\textcolor{teal}{Calibration refers to the statistical consistency between the distributional forecasts and the observations. It measures how well the predicted probabilities match the actual. On the other hand, sharpness refers to the concentration of the forecast distributions --- a sharp forecast distribution results in narrow prediction intervals, indicating high confidence in the forecast. A model is well-calibrated if the predicted probabilities match the actual, and it is sharp if it is confident in its predictions. The CRPS rewards sharpness and calibration by assigning lower scores to forecasts with sharper distributions, and to forecasts that are well-calibrated. Thus, it is a metric that combines both sharpness and miscalibration into a single score, making it a useful tool for evaluating the performance of probabilistic forecasts.}

@@

_Comment 8: Section 4.2 does not sufficiently relate to the current problem at hand. The definitions presented are given in a standard form without providing context or explaining how they relate to the problem or dataset being analyzed. For example, the term ”bottom-level series” is used in both the text and Table 2, but it is not clear how this term applies to the specific dataset being studied. It would be beneficial to provide a concrete example from the dataset to help readers understand the concept of ”bottom-level series” in the context of this problem._

**Response:** We agree that further explanation of the definitions presented in Section 4.2 would be beneficial for readers. In particular, we will provide an example from our dataset to illustrate the concept of "bottom-level series" and how it applies to our problem. We have ioncluded the following text in the revised version of the manuscript to address this comment:.

\textcolor{teal}{The term "level bottom series" relates to the most disaggregated series within the hierarchical and grouped time series structure. For instance, in Table 2, each distinct combination of values in Control area (e.g. South \& East), Health board (e.g. CV), Priority (e.g. Green), and Nature of incident (e.g. Chest pain) corresponds to one individual time series. In the dataset at hand, there are 691 unique combinations, resulting in 691 bottom level time series. The "aggregate time series" describes how these bottom-level series are combined to create higher-level series. For instance, to obtain the incidents at the national level (i.e. all country level), the time series are aggregated across all Control areas, Health boards, Priorities, and Natures of incidents. Any desired aggregation level can be achieved based on the data structure, utilizing the bottom level series available.}

@@

_Comment 9: I am experiencing confusion while reading section 4.2.2. The section discusses a ”bottom-up approach” and it sounds like it is not a favorable approach. However, in the following paragraph, you mention ”forecast reconciliation approaches.” Are these two different approaches or is the ”forecast reconciliation approach” a type of ”bottom-up approach”? Additionally, you also mention the use of ”linear reconciliation method” in this section, which leads me to assume it is a type of ”forecast reconciliation approach.” Can you provide further clarification on these different approaches and how they relate to each other in this context?_

**Response:** We apologize for any confusion that may have arisen from the text. Please allow us to provide some clarification.

While the bottom-up approach does lead to coherent forecasts, it is not a forecast reconcilation approach because no reconciling is done. In the bottom-up approach, forecasts are generated at the bottom (most disaggregate) level and then aggregated up to higher levels in the hierarchy. This approach has limitations because it only uses base forecasts from a single level of aggregation at the bottom level. On the other hand, the linear reconciliation method uses all base forecasts generated within a hierarchical structure to regenerate coherent forecasts at all level of the hierarchy. This means that it does not only use base forecasts from a single level of aggregation, but rather uses all available information at all levels to generate forecasts that minimises the total forecast variance of the set of coherent forecasts. We hope this clarifies the difference between the two approaches and how they relate to each other in the context of the paper. There are also different approaches in the linear reconciliation method, we have now updated section 4.4 and included the following paragraphs to address your cocnerns:

\textcolor{teal}{The bottom-up (BU) approach is constrained by its reliance solely on base forecasts from a single level of aggregation at the bottom level. While it does result in consistent forecasts, the BU approach lacks forecast reconciliation since no reconciliation is performed.}

\textcolor{teal}{Forecast reconciliation approaches bridge this gap by combining and reconciling all base forecasts to generate coherent forecasts. This technique utilizes all the base forecasts produced within a hierarchical structure to create consistent forecasts at every level of the hierarchy. As a result, it goes beyond relying solely on base forecasts from a single level of aggregation, and instead leverages all available information at each level to generate forecasts that minimize the total forecast variance of the set of coherent forecasts.}

\textcolor{teal}{Ordinary Least Squares (OLS) is the simplest and most commonly used method for estimating the parameters in linear regression models. In this approach, the estimation of W is based on the assumption that all the errors have equal variance. Hence, W is simply defined as the identity matrix multiplied by a constant factor. The intuition behind OLS is that it minimizes the sum of squared residuals between the observed and predicted values of the dependent variable. The main weakness of this approach is that it does not take account of the different scales of the base time series; the aggregated series will usually have higher variance than the disaggregated series, simply because the values are larger, but OLS treats all series the same. A strength of the approach is that it is simple, and does not involve estimating a covariance matrix.}

\textcolor{teal}{Weighted Least Squares (WLS) is an extension of OLS where the variance of the errors is assumed to be heteroscedastic, i.e., different for each series. But it assumes that the errors of each series are uncorrelated with each other. In this approach, W is defined as a diagonal matrix with the variance of the errors on the diagonal. The intuition behind WLS is that it assigns higher weight to series with smaller error variance, and thereby takes into account the different scales of the base time series. The main weakness of this approach is that it ignores the relationships between series. A strength of WLS is that it is relatively easy to compute W as it is based only on error variances which are readily estimated.}

### 2023-07-18 journal_correspondence/response_letter/response_letter_JSR.qmd

\textcolor{teal}{Minimum Trace (MinT) is a further generalization where W is defined as the covariance matrix of the base forecast errors. So it takes account of both the scale of each series, and the relationships between the series.} @WicEtAl2019 \textcolor{teal}{showed that this approach gives the optimal reconciled forecasts in the sense that the sum of the forecast variances is minimized. The main weakness of this approach is that it is difficult to estimate the full covariance matrix. In practice, we usually need to use a shrinkage estimate where the off-diagonal elements are shrunk towards zero.}

@@

_Comment 10: In section 5, you present the results of your research. From my understanding, the ”forecast reconciliation approach” aggregates lower-level forecasts. If this understanding is correct, I am confused as to why you are comparing base forecasts to the aggregation of those base-level forecasts as they appear to be fundamentally different things. Also, in the second paragraph of page 20, you mention that the reconciliation may not improve the forecast accuracy if the bottom series are ”noisy” and lack systematic patterns. My question is: in such cases, what is the purpose or benefit of performing reconciliation at the bottom level?_

**Response:** Thank you for the comment.

The forecast reconciliation approach does not aggregate lower level forecasts, instead it combines all base forecasts. The base forecasts are generated independently at each level of the hierarchy, ignoring the hierarchical/grouped structure of time series or any aggregation constraints. As a result, the base forecasts are not guaranteed to be coherent, meaning that the sum of the lower-level forecasts will not necessarily add up to the higher-level forecast. On the other hand, the forecast reconciliation approach takes the base forecasts and regenerates them in a way that ensures coherence across all levels of the hierarchy, while also considering all available information. The comparison between the base forecasts and the reconciled forecasts allows us to see the improvement in forecast accuracy that can be achieved by using the forecast reconciliation approach.

While the approach is designed to improve forecast accuracy, it may not always be successful in doing so, particularly if the bottom-level series are too noisy and lack systematic patterns. In such cases, the benefit of performing reconciliation at the bottom level may still lie in creating coherent forecasts that can help align planning across different teams in an organization, improve coordination, and avoid conflicting decisions. Additionally, even if the bottom-level series are noisy and lack systematic patterns, reconciliation can still lead to more accurate forecasts at higher levels of the hierarchy by utilizing the information available across the hierarchy. Therefore, even if the bottom-level forecasts might not be very accurate on their own, reconciling them with higher-level forecasts can still provide a more consistent view of future demand and possibly more accurate forecasts at other levels.

We have added the following paragraph in the revised version of the manuscript to address this comment:

\textcolor{teal}{While the forecast reconciliation approach aims to enhance forecast accuracy, its effectiveness may not always be guaranteed, especially if the bottom-level series exhibit excessive noise and lack systematic patterns. Despite this, reconciling forecasts at the bottom level can offer advantages by generating coherent forecasts that facilitate alignment in planning across various teams within an organization, promote better coordination, and prevent conflicting decisions. Moreover, even when dealing with noisy and irregular bottom-level series, reconciliation can still improve forecast accuracy at higher levels of the hierarchy by leveraging the information available across the hierarchy. Therefore, although the bottom-level forecasts may not be highly accurate on their own, reconciling them with higher-level forecasts can still provide a more consistent view of future demand and potentially yield more accurate forecasts at other levels.}

@@

_Comment 11: In the second to last sentence of the paper, you state that ”the reconciled forecast distributions are not counts.” In your evaluation of forecast performance, did you round any of these non-integer values to whole numbers or were they kept as non-integers? For practical implementation, it is necessary to round these non-integers to whole numbers. Have you considered how your forecasting approaches perform if the non-integer forecast results are rounded up or rounded down?_

**Response:** Thank you for highlighting this point, we have now included a paragraph at the end of the result section to acknowledge this point.

Rounding forecasts up or down and its effect on the forecast accuracy depends on the level of hierarchy and scale of data. For some situations, with high volume demand, forecast accuracy calculations can ignore integer effects as rounding becomes negligible. However, low volume demand settings, such as forecasts at the bottom level of the hierarchy, may be more susceptible to integer (rounding) effects. In practice, we may need to use integer forecasts, especially when the forecasts are relatively small. Count forecast reconciliation is an active area of research, and it would be interesting to explore in future research how our approach could be adapted to generate count reconciled probabilistic forecasts.

\textcolor{teal}{Despite using Poisson regression models to create count distributions of attended incidents for the base forecasts, it is important to note that the reconciled forecast distributions do not maintain a count format. In practical scenarios, there might be a need to use integer forecasts. Count forecast reconciliation is an active area of research, and it would be interesting to explore how our approach could be adapted to generate count-reconciled probabilistic forecasts in future studies. One possible approach to address this is by rounding the forecasts. However, the impact of rounding on forecast accuracy varies depending on the level of hierarchy and the scale of the data. In situations with high-volume demand, the effects of rounding may become negligible, and forecast accuracy calculations can overlook integer effects. On the other hand, in low-volume demand settings, such as forecasts at the bottom level of the hierarchy, integer (rounding) effects may have a more noticeable influence on forecast accuracy.}

@@

_Comment 12: In Table 1, the number of parameters for “Priority * Nature of incident” is 104. Why is it not 105? Similar questions for the next two rows._

**Response:** The reason for the discrepancy in the number of series is that for some combinations of priority and nature of incidents, there is no representation in the dataset. Therefore, these combinations are not included in the table. For example, in the "Priority * Nature of incident" combination, one of the cells in the cross-tabulation has no incidents recorded for the combination of Red Green priority and Falls, so it is not included in the dataset. The same reasoning applies to the other two combinations in Table 1. we have added a note to Table 1 to explain this further. Please refer to Table 1 in the revised paper.

@@

_General comment: This paper proposes hierarchical algorithms to forecast the Emergency Medical Services (EMS) demands with both point estimates and distributional estimates. The EMS count data are naturally structured with hierarchies (with spatial levels corresponding to nation, sub-nation and region) and groups (including the priority and incident of the demand).  The author starts with independent/base forecast with some classical benchmark time series algorithms such as moving average, GLM and Poisson regression. The hierarchical forecasts are then introduced with the bottom-up structure and optimal reconciliation approaches. The outperformance of the algorithm is demonstrated by comparing the accuracy between combinations of methods and models under different spatial levels and groups. I appreciate the detailed background introduction and literature review for the application topic. The novel point of view that introduces the hierarchical and grouped forecasts to the EMS management community is promising. I provide some main suggestions, questions and minor comments listed below for reference._

**Response:** Thank you for your detailed review and positive feedback on our paper. We appreciate your valuable suggestions, questions, and comments, and we will address them accordingly.

_Comment 1: Section 3.2 of Forecasting methods covers the independent/base forecasting methods, and Section 3.3 of Performance evaluation is designed for both base and grouped forecasts. I would suggest to look further into the logic structure of Sections 3 and 4. One advice may be to push back the overview of base forecast algorithms (Section 3.2) to a new section before the main contribution of grouped forecasts in Section 4._

**Response:** Thank you for your valuable suggestion to enhance the paper's structure. We have thoroughly considered your proposal of moving the base forecast to a new section. However, after careful consideration, we believe that the current structure maintains a smooth and easily understandable flow. As it stands, Section 3 provides a detailed discussion of the forecasting models, while Section 4 focuses on using the models described in Section 3 to generate forecasts for the hierarchical structure, including both base and reconciled forecasts. We hope this arrangement aligns with your expectations and requirements.

@@

_Comment 2: In Section 3.2, the author builds the base forecasting models._
_Comment 2-1: There should be more detail added to ETS and Ensemble method. What exactly do they do? Ensemble method refers to Wang et al., but no specific reference. Adding explanatory details to the used methods and a short discussion on other methods should be sufficient._

**Response:**  In the revised version, we have added more detailed explanations on ETS, Ensemble as well as Naive, GLM and TSGLM. Please refer to section 3.2 to see all details:

We added the following text in the revised version of the manuscript:

\textcolor{teal}{In our study, we use an automated algorithm to determine the suitable form for the trend, seasonality, and error terms in each time series. Specifically, we utilize the `ETS()` function in the fable package of R, which employs statistical criteria like Akaike's Information Criterion (AIC) to identify the optimal model for each time series. Given the large number of time series we work with (1530), it is impractical to manually select the appropriate form for each component in every time series. Consequently, the automated algorithm selects the most fitting components based on the unique characteristics of each individual time series. As a result, a combination of additive or multiplicative forms for the components are employed, depending on the specific attributes of each time series.}

\textcolor{teal}{Finally, one effective strategy for improving forecast accuracy includes the simultaneous application of multiple forecasting methods on a given time series, followed by averaging the forecasts, rather than relying on separate forecasts generated by each individual method} [@clemen1989combining]. \textcolor{teal}{In this paper, we use an ensemble method that combines the forecasts generated from the Naive, ETS, GLM and TSGLM models using a simple average to form a mixture distribution} [@combinations].

For the rest of the methods, we added:

\textcolor{teal}{We have chosen the naive method as a benchmark due to its widespread usage and simplicity, making it easily understandable for users. Forecasts serve as inputs for various decision-making systems that frequently employ simulations, wherein it is common to utilize the empirical distribution of demand as a forecast. Additionally, the naive method has shown surprisingly high accuracy. Hence, any forecasting approach that can offer superior results compared to the naive method would validate its practical use, otherwise there is no necessity for employing more complex methods.}

\textcolor{teal}{Suppose the time series is denoted by $y_1,\dots,y_T$, then the Poisson GLM can be written as}

\begin{align*}
  y_t &\sim \text{Poisson}(\lambda_t) \\
  \text{where}\qquad
  \log(\lambda_t) &= \bm{x}_t'\bm{\beta},
\end{align*}

\textcolor{teal}{and $\bm{x}_t$ is a vector of covariates, $\beta$ is a vector of coefficients, and $\lambda_t$ is the parameter of Poisson distribution. In our model, these include cubic splines for the time trend, day-of-week dummy variables (from Monday to Sunday), Fourier terms to capture the yearly seasonality, dummy variables indicating public holidays (1 when is public holiday, 0 otherwise), school holidays (1 when is school holiday, 0 otherwise) and Christmas Day (1 when is Christmas Day, 0 otherwise) and New Year's Day (1 when is New Year's Day, 0 otherwise). The Fourier terms are as defined in} @hyndman2021forecasting \textcolor{teal}{(Section 7.4). This model takes account of weekly seasonality and annual seasonality. Monthly seasonality is exceedingly rare in time series data, and does not occur in ambulance demand. There is no reason, for example, for incidents to occur more at some times of the month than others.}

\textcolor{teal}{The Poisson TSGLM is similar to GLM with an additional component accounting for serial correlation (i.e. autoregressive). The term serial dependence refers to situations where the ambulance demand at a given time point exhibits correlation with the demand at previous time points. Put simply, past values of the time series influence the current values, and various techniques can be employed to model this influence. TSGLM can be written as}

\begin{align*}
  y_t &\sim \text{Poisson}(\lambda_t) \\
  \text{where}\qquad
  \log(\lambda_t) &= (\bm{y}_{t-k}'+\bm{x}_t')\bm{\beta},
\end{align*}

\textcolor{teal}{${y}_{t-k}$ is a vector of k lagged values. The TSGLM model explicitly accounts for serial dependence by including lagged values (i.e. past values) of the ambulance demand in the model. This is important in EMS forecasting because it allows the model to capture patterns in the data that are dependent on the past values of the time series, which might not be captured via the predictor variables.}

\textcolor{teal}{We use the `tsglm()` function in the `tscount` package in R} [@JSSv082i05] \textcolor{teal}{to model the attended incidents. Again, the logarithmic link function is used to ensure that the parameter of Poisson distribution is always positive.}

@@

_Comment 2-2: In ETS, there are trend, seasonality and a property about the error terms. Have all combination options been considered? If not, how has it been evaluated?_

**Response:** Since we had a large number of time series (1530), we did not manually evaluate all possible combinations of trend, seasonality, and error terms in ETS for each time series. Instead we used an automatic algorithm to select the most appropriate model for each time series based on statistical criteria such as Akaike's Information Criterion (AIC). The automatic algorithm considered a mix of different component forms, depending on the specific characteristics of each time series. We have added additional details on the automatic algorithm used in the revised version of the paper.

We added the following text in the revised version of the manuscript to address this comment:

\textcolor{teal}{In our study, we use an automated algorithm to determine the suitable form for the trend, seasonality, and error terms in each time series. Specifically, we utilize the `ETS()` function in the fable package of R, which employs statistical criteria like Akaike's Information Criterion (AIC) to identify the optimal model for each time series. Given the large number of time series we work with (1530), it is impractical to manually select the appropriate form for each component in every time series. Consequently, the automated algorithm selects the most fitting components based on the unique characteristics of each individual time series. As a result, a combination of additive or multiplicative forms for the components are employed, depending on the specific attributes of each time series.}

@@

_Comment 2-3: GLM and TSGLM are regression approaches, sometimes with exogenous variables like holiday indicators. I would suggest to include explicit model formulas (probably R-formatted like y ~ a + b + c) to list all the input predictors._

**Response:** We have revised the manuscript to include the model formulas, as you suggested for both GLM and TSGLM. We have also included the entire publication in Quarto, including R codes, in a GitHub repository for further details:

\textcolor{teal}{Suppose the time series is denoted by $y_1,\dots,y_T$, then the Poisson GLM can be written as}

\begin{align*}
  y_t &\sim \text{Poisson}(\lambda_t) \\
  \text{where}\qquad
  \log(\lambda_t) &= \bm{x}_t'\bm{\beta},
\end{align*}

\textcolor{teal}{and $\bm{x}_t$ is a vector of covariates, $\beta$ is a vector of coefficients, and $\lambda_t$ is the parameter of Poisson distribution. In our model, these include cubic splines for the time trend, day-of-week dummy variables (from Monday to Sunday), Fourier terms to capture the yearly seasonality, dummy variables indicating public holidays (1 when is public holiday, 0 otherwise), school holidays (1 when is school holiday, 0 otherwise) and Christmas Day (1 when is Christmas Day, 0 otherwise) and New Year's Day (1 when is New Year's Day, 0 otherwise). The Fourier terms are as defined in} @hyndman2021forecasting \textcolor{teal}{(Section 7.4). This model takes account of weekly seasonality and annual seasonality. Monthly seasonality is exceedingly rare in time series data, and does not occur in ambulance demand. There is no reason, for example, for incidents to occur more at some times of the month than others.}

\textcolor{teal}{The Poisson TSGLM is similar to GLM with an additional component accounting for serial correlation (i.e. autoregressive). The term serial dependence refers to situations where the ambulance demand at a given time point exhibits correlation with the demand at previous time points. Put simply, past values of the time series influence the current values, and various techniques can be employed to model this influence. TSGLM can be written as}

\begin{align*}
  y_t &\sim \text{Poisson}(\lambda_t) \\
  \text{where}\qquad
  \log(\lambda_t) &= (\bm{y}_{t-k}'+\bm{x}_t')\bm{\beta},
\end{align*}

\textcolor{teal}{${y}_{t-k}$ is a vector of k lagged values. The TSGLM model explicitly accounts for serial dependence by including lagged values (i.e. past values) of the ambulance demand in the model. This is important in EMS forecasting because it allows the model to capture patterns in the data that are dependent on the past values of the time series, which might not be captured via the predictor variables.}

\textcolor{teal}{We use the `tsglm()` function in the `tscount` package in R} [@JSSv082i05] \textcolor{teal}{to model the attended incidents. Again, the logarithmic link function is used to ensure that the parameter of Poisson distribution is always positive.}

@@

_Comment 3: Section 3.3 stakes different measures for performance evaluation. I suggest to give more detailed references opposed to just the paper, i.e., equation numbers._

**Response:** We have revised the manuscript to include a more detailed reference for each equation used in the performance evaluation. Specifically, we have included the paper citation along with the equation number, so that readers can easily locate the relevant equation and read more about its derivation and interpretation. Please refer to section 3.3 to see changes, also highlighted below:

\textcolor{teal}{The error metrics provided below consider a forecasting horizon denoted by j, representing the number of time periods ahead we are predicting. In our study, this forecasting horizon ranges from 1 to 84 days, $j= 1,2,\dots, 84$.}

\textcolor{teal}{Using of scale-independent measures, such as MASE and MSSE, enables more significant comparisons between time series at different levels and scales, as these measures are not influenced by the data's magnitude. This aspect holds particular importance in our study, as we work with time series at various levels of hierarchy. These time series show varying scales, resulting in different magnitudes of error. By employing scale-independent measures, we can meaningfully assess the forecast accuracy across the entire hierarchy, ensuring a more robust comparison.}

\textcolor{teal}{Calibration refers to the statistical consistency between the distributional forecasts and the observations. It measures how well the predicted probabilities match the actual. On the other hand, sharpness refers to the concentration of the forecast distributions --- a sharp forecast distribution results in narrow prediction intervals, indicating high confidence in the forecast. A model is well-calibrated if the predicted probabilities match the actual, and it is sharp if it is confident in its predictions. The CRPS rewards sharpness and calibration by assigning lower scores to forecasts with sharper distributions, and to forecasts that are well-calibrated. Thus, it is a metric that combines both sharpness and miscalibration into a single score, making it a useful tool for evaluating the performance of probabilistic forecasts.}

@@

_Comment 4: The author extracts the trend and weekly seasonality of the data, and demonstrates their strengths in Figure 2. The follow-up analysis and forecast depend on the Poisson assumption most of the time due to the nature of non-negative count time series data. Is there any verification conducted to confirm the Poisson patterns in the data? Are over-dispersion and/or under-dispersion going to be potential issues? It may suffice to include statements from relative references._

**Response:** Thank you for your comment. Provided accidents occur independently, they will follow a Poisson distribution by definition (@feller1991introduction, p156-158). So it is reasonable to assume a Poisson distribution here. We allow for the mean of the Poisson distribution to change over time by including trend and seasonality covariates, and public holiday effects. If there are other factors that affect the mean of the Poisson distribution, but which aren't in our model, we may observe over-dispersion or under-dispersion. We have developed a flexible framework that can incorporate any forecasting model, and it is important to note that the intention of this paper is not to provide a comprehensive list of models, or to argue for a particular model class. Instead, our focus is on demonstrating the usefulness of our framework for incorporating base forecasts generated by any model and producing hierarchical coherent forecasts.

To address this comment, we have added the following to section 3 before ensemble method:
